---
title: "VCFArray: DelayedArray objects with on-disk/remote VCF backend"
author:
- name: Qian Liu
  affiliation: Roswell Park Comprehensive Cancer Center, Buffalo, NY
- name: Valerie Obenchain
  affiliation: Fred Hutchinson Cancer Research Center, Seattle, WA
- name: Martin Morgan
  affiliation: Roswell Park Comprehensive Cancer Center, Buffalo, NY
date: "last edit: 08/22/2018"
output:
    BiocStyle::html_document:
        toc: true
        toc_float: true
package: VCFArray
vignette: >
  %\VignetteIndexEntry{VCFArray: DelayedArray objects with on-disk/remote VCF backend}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r options, eval=TRUE, echo=FALSE}
options(showHeadLines=3)
options(showTailLines=3)
```
```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction 
[VCFArray][] is a _Bioconductor_ package that represents VCF files as
objects derived from the [DelayedArray][] package and `DelayedArray`
class. It converts data entries from VCF file into a
`DelayedArray`-derived data structure. The backend VCF file could
either be saved on-disk locally or remote as online resources. Data
entries that could be extracted include the fixed data fields (REF,
ALT, QUAL, FILTER), information field (e.g., AA, AF...), and the
individual format field (e.g., GT, DP...). The array data generated
from fixed/information fields are one-dimensional `VCFArray`, with the
dimension being the length of the variants. The array data generated
from individual `FORMAT` field are always returned with the first
dimension being `variants` and the second dimension being
`samples`. This feature is consistent with the assay data saved in
`SummarizedExperiment`, and makes the `VCFArray` package interoperable
with other established _Bioconductor_ data infrastructure.

[VCFArray]: https://bioconductor.org/packages/VCFArray
[DelayedArray]: https://bioconductor.org/packages/DelayedArray

# Installation

1. Download the package. 

```{r getPackage, eval=FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install("VCFArray")
```
The development version is also available to download from Github. 
```{r getDevel, eval=FALSE}
BiocManager::install("Liubuntu/VCFArray")
```

2. Load the package into R session.
```{r Load, message=FALSE}
library(VCFArray)
```

# VCFArray

## VCFArray, VCFMatrix
`VCFArray` represents VCF files as `DelayedArray` instances. It has
methods like `dim`, `dimnames` defined, and it inherits array-like
operations and methods from `DelayedArray`, e.g., the subsetting
method of `[`.

## Internals: VCFArraySeed 

# sessionInfo()

```{r}
sessionInfo()
```
