1. bug in document(). error returns for VCFArray(seed) after document(): 

-- issue identified as bug in `devtools`: https://github.com/r-lib/devtools/issues/1845
-- workaround now. export `DelayedUnaryOp` and `DelayedOp` classes from `DelayedArray` package (locally modified and installed. install.packages("/home/qian/Documents/Research/DelayedArray", repos=NULL)).

```{r}
seed <- VCFArraySeed(fl, name = "GL")
VCFArray(seed)
## Error in validObject(.Object) : invalid class “DelayedMatrix” object: 
##     'x' must have exactly 2 dimensions
traceback()
## 10: stop(msg, ": ", errors, domain = NA)
## 9: validObject(.Object)
## 8: initialize(value, ...)
## 7: initialize(value, ...)
## 6: new(...)
## 5: new2(Class, seed = seed)
## 4: new_DelayedArray(seed, Class = "VCFArray") at VCFArray-class.R#104
## 3: DelayedArray(seed)
## 2: DelayedArray(seed) at VCFArray-class.R#131
## 1: VCFArray(seed)
```

2. Remove the `Rsamtools` from `DESCRIPTION, Imports` for now. Because the `Rsamtools::countTabix()` function is remove from our script.   -- done!

3. VCFArraySeed(file = "VCFFile")  -- done!
- if (!is.na(index(file)) && length(index)) stop()
- if (is.na(index(file)) && length(index) ) index(file) = index
- if (is.na(index(file)) && !length(index) ) index(file) = paste0(path(file), ".tbi")

4. save header info into `VCFArraySeed`. 
- to extract the header info, geno(header)$Type in `extract_array`.  -- done!
- fail later if `VCFArray(name=NULL)` in `VCFArraySeed(name = )` checking.   -- done!
- extract the possible 3rd dimension of `VCFArraySeed` and save as @dim slot. -- done!
  
5. VCFArraySeed(file = "VCFStack")
- Check ?readVcfStack: lapply to each individual VCFFile and then rbind the VCF files. 
- use readVCFStack(param = ) in VCFArraySeed() constructor.   -- done!
- only takes in `RangedVcfStack` object, because it has the rowRanges() available, which is required for the `VCFArraySeed` constructor. -- done!

6. **BUG**: show method for >2 dimensional array. 
   bug report: https://github.com/Bioconductor/DelayedArray/issues/25
```{r}
rgstack
seed <- VCFArraySeed(rgstack, name="SB")
index <- list(1:2, NULL, NULL)
extract_array(seed, index)
index <- list(seq(to=nrow(seed), length.out=2), NULL, NULL)
extract_array(seed, index)
VCFArray(seed)  ## ERROR
```

7. How about the other data inside VCF? 
- rowData(): REF,ALT, QUAL, FILTER, paramRangeID?
- info(AC, AF, AN, DB, DP, FS, QD, ...)

1) header(fl/VcfFile)
2) name %in% rownames(info(header)), 
	readVcf(vcffile(seed), param = ScanVcfParam(info = name, fixed = NA, geno = NA, which = ...))
3) name %in% names(fixed(header))
	readVcf(vcffile(seed), param = ScanVcfparam(fixed = name, info = NA, geno = NA, which = ...))


Martin: 

1. add method of scanVcfHeader::VcfStack, to return the shared header info for all VcfFile objects inside the VcfStack object. 



